Efficiently summarising relationships in large samples: a general duality between statistics of genealogies and genomes

### 2019-08-01 treestats_paper.tex
new fig

>>>>

An example is shown in Figure~\ref{fig:branch_site_diagram},
showing how the $f_4$ site statistic assigns a weight to each mutation
depending on the frequencies in each of the four sample sets below it,
and how the corresponding branch statistic assigns the same weight to those branches.

\begin{figure}
    \centering
    \includegraphics{figures/branch_site_diagram}
    \caption{
    Computing the $f_4(A,B;C,D)$ statistic on a tree.
    \textbf{(a)} Each mutation is given weight equal to $(p_A - p_B)(p_C - p_D)$,
    where $p_X$ is the proportion of the samples inheriting that mutation in set $X$
    (shown in labels at the bottom).
    Note that each of the mutations shown occurs at a distinct site, so there is no backmutation.
    \textbf{(b)} Each branch is assigned weight equal to the weight that would be assigned
    to any mutation falling in it, and then the branch $f_4$ statistic
    is the sum over these weights, multiplied by the length of the branch
    (and the span of the tree, not depicted).
        \label{fig:branch_site_diagram}
    }
\end{figure}
